---
title: "Tidyverse_20190918_717_oh"
output: 
  rmdformats::readthedown:
    highlight: kate
---
# 3.The tidyverse: using dataframe {#tidyverse}
지금까진 vector로 reorder, subset, index했었지만

지금부터는 data.frame으로 다루는 법을 배웁시다.

배우기 앞서 _tidy_에 대해서 쉽게 때려넣으면
**표준화된 data.frame임**
데이터 처리에 가장 많은 시간이 소요되는 전처리 과정을 줄여 보자, 그러기 위해 처음부터 데이터를 표준화해서 만들자는 것임.

**깔끔한 데이터(Tidy data)의 특징**

1\. 각 변수는 개별의 열(column)으로 존재한다.  
2\. 각 관측치는 행(row)를 구성한다.  
3\. 각 표는 단 하나의 관측기준에 의해서 조직된 데이터를 저장한다.  
4\. 만약 여러개의 표가 존재한다면, 적어도 하나이상의 열(column)이 공유되어야 한다.  
5\. long format: row만 길고 column수는 적어 column을 추가하기 쉬움
**더러운 데이터(NOT Tidy)의 특징**

1\. 열 이름(Column header)이 변수 이름이 아니고 값인 경우  
2\. 같은 표에 다양한 관측 단위(observational units)가 있는 경우  
3\. 하나의 열(column)에 여러 값이 들어 있는 경우  
4\. 변수가 행과 열에 모두 포함되어 있는 경우   
5\. 하나의 관측 단위(observational units)가 여러 파일로 나누어져 있는 경우  
6\. wide format: column수가 많은 것으로 위의 5번과 비교!

궁금하면 Jeff Leek가 쓴 [The Elements of Data Analytic Style](vita.had.co.nz/papers/tidy-data.pdf)
보셈

We will be using data frames for the majority of this book. We will focus on a specific data format referred to as _tidy_ and on specific collection of packages that are particularly helpful for working with _tidy_ data referred to as the _tidyverse_.


We can load all the tidyverse packages at once by installing and loading the __tidyverse__ package:

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
```

We will learn how to implement the tidyverse approach throughout the book, but before delving into the details, in this chapter we introduce some of the most widely used tidyverse functionality, starting with the __dplyr__ package for manipulating data frames and the __purrr__ package for working with functions. Note that the tidyverse also includes a graphing package, __ggplot2__, which we introduce later in Chapter \@ref(ggplot2) in the Data Visualization part of the book; the __readr__ package discussed in Chapter \@ref(importing-data); and many others. In this chapter, we first introduce the concept of _tidy data_ and then demonstrate how we use the tidyverse to work with data frames in this format. 

## 3.1 Tidy data {#tidy-data}: 'tidy하다'라는게 뭘까?
We say that a data table is in  _tidy_ format if each row represents one observation and columns represent the different variables available for each of these observations. The `murders` dataset is an example of a tidy data frame.

```{r, echo=FALSE}
library(dslabs)
murders
data(murders)
head(murders)
```
여기서 
row: state 
Columns:5개: name, abbreviation, region, population, total murders

결론: Tidy함

To see how the same information can be provided in different formats, consider the following example:

```{r, echo=FALSE}
library(dslabs)
data("gapminder")
tidy_data <- gapminder %>% filter(country %in% c("South Korea", "Germany") & !is.na(fertility)) %>%
  select(country, year, fertility)
head(tidy_data, 6)
```

This tidy dataset provides fertility rates for two countries across the years. This is a tidy dataset because each row presents one observation with the three variables being country, year, and fertility rate. However, this dataset originally came in another format and was reshaped for the __dslabs__ package. Originally, the data was in the following format:


```{r, echo=FALSE, message=FALSE}
path <- system.file("extdata", package="dslabs")
filename <- file.path(path, "fertility-two-countries-example.csv")
wide_data <- read_csv(filename)
select(wide_data, country, `1960`:`1962`) %>% as.data.frame
```

The same information is provided, but there are two important differences in the format: 

```
1) each row includes several observations 
2) one of the variables, year, is stored in the header. 
```
For the tidyverse packages to be optimally used, data need to be reshaped into `tidy` format, which you will learn to do in the Data Wrangling part of the book. Until then, we will use example datasets that are already in tidy format.

Although not immediately obvious, as you go through the book you will start to appreciate the advantages of working in a framework in which functions use tidy formats for both inputs and outputs. You will see how this permits the data analyst to focus on more important aspects of the analysis rather than the format of the data. 

## Exercises  
1\. Examine the built-in dataset `co2`. Which of the following is true:
```{r}
co2
class(co2)
```
a. `co2` is tidy data: it has one year for each row.  
b. `co2` is not tidy: we need at least one column with a character vector.  
**c. `co2` is not tidy:  it is a matrix instead of a data frame.**  
d. `co2` is not tidy: to be tidy we would have to wrangle it to have three columns (year, month and value), then each co2 observation would have a row.  

2\. Examine the built-in dataset  `ChickWeight`. Which of the following is true:
```{r}
ChickWeight
class(ChickWeight)
```
a.  `ChickWeight` is not tidy: each chick has more than one row.  
**b.  `ChickWeight` is tidy: each observation (a weight) is represented by one row. The chick from which this measurement came is one of the variables.**  
c.  `ChickWeight` is not tidy: we are missing the year column.  
d.  `ChickWeight` is tidy: it is stored in a data frame.  


3\. Examine the built-in dataset `BOD`. Which of the following is true:
```{r}
BOD
```

a. `BOD` is not tidy: it only has six rows.  
b. `BOD` is not tidy: the first column is just an index.  
**c. `BOD` is tidy: each row is an observation with two values (time and demand)**  
d. `BOD` is tidy: all small datasets are tidy by definition.  


4\. Which of the following built-in datasets is tidy (you can pick more than one):

```{r}
#tidy하기 위해선.. data.frame성격을 가져야하니. class()로 파악
class(BJsales)
class(EuStockMarkets)
class(DNase)
class(Formaldehyde)
class(Orange)
class(UCBAdmissions)

```

```{r}
#DNase, Formaldehyde, Orange, UCBAdmissions을 View()로 보자.
DNase
Formaldehyde
Orange
UCBAdmissions
# DNase는 run값들이 구별이 쉽지않아 탈락
# Formaldehyde는 합격 carb값에 따른 opt값으로 경향성 파악가능
# Orange도 역시 tree값들 구별 안되서 탈락
# UCBAdmissions은 합격 각각 row값에 따른 column값들 파악 가능
```

a. `BJsales`  
b. `EuStockMarkets`  
c. `DNase`  
**d. `Formaldehyde`**  
e. `Orange`  
**f. `UCBAdmissions`**  


## 3.2 Manipulating data frames

The __dplyr__ package from the __tidyverse__ introduces functions that perform some of the most common operations when working with data frames and uses names for these functions that are relatively easy to remember. For instance, to change the data table by adding a new column, we use `mutate`.  To filter the data table to a subset of rows, we use `filter`. Finally, to subset the data by selecting specific columns, we use `select`.

### 3.2.1 Adding a column: `mutate()`

We want all the necessary information for our analysis to be included in the data table. So the first task is to add the murder rates to our murders data frame.

`mutate`구조
`mutate(\argument:data.frame이름\, \new column name\ = \value, formular, 파일위치 등등\)`

So, to add murder rates, we use:
 
```{r, message=FALSE}
library(dslabs)
data("murders")
#아래처럼 mutate하고 `murders <-`로 해야 업데이트 됨.
#결과값을 비교해보요.
mutate(murders, rate = total / population * 100000)
murders
murders <- mutate(murders, rate = total / population * 100000)
murders
```

Notice that here we used `total` and `population` inside the function, which are objects that are **not** defined in our workspace. But why don't we get an error?

This is one of __dplyr__'s main features. Functions in this package, such as `mutate`, know to look for variables in the data frame provided in the first argument. In the call to mutate above, `total` will have the values in `murders$total`. This approach makes the code much more readable. 

We can see that the new column is added:

```{r}
head(murders)
```

Although we have overwritten the original `murders` object, this does not change the object that loaded with `data(murders)`. If we load the `murders` data again, the original will overwrite our mutated version.

### 3.2.2 Subsetting: `filter()`

Now suppose that we want to filter the data table to only show the entries for which the murder rate is lower than 0.71. To do this we use the `filter` function

`filter`구조
`filter(\argument:data.frame이름\, \column name\ \=\ \value, formular등등)`

Like `mutate`, we can use the unquoted variable names from `murders` inside the function and it will know we mean the columns and not objects in the workspace.

```{r}
filter(murders, rate <= 0.71)
```


### 3.2.3 Selecting columns: `select()`

Although our data table only has six columns, some data tables include hundreds. If we want to view just a few, we can use the __dplyr__ `select` function. 

`select`구조
`select(\argument:data.frame이름\, \column_name1\,\column_name2\,\column_name3\...)`


In the code below we select three columns, assign this to a new object and then filter the new object: 

```{r}
#뉴 테이블에 select한 Column만 담기
new_table <- select(murders, state, region, rate)
new_table
#다시 `filter()`써서 추려내기
filter(new_table, rate <= 0.71)
```

In the call to `select`, the first argument `murders` is an object, but `state`, `region`, and `rate` are variable names. 

## Exercises 
1\. Load the __dplyr__ package and the murders dataset.

```{r, eval=FALSE}
library(dplyr)
library(dslabs)
data(murders)
```

You can add columns using the __dplyr__ function `mutate`. This function is aware of the column names and inside the function you can call them unquoted:


```{r, eval=FALSE}
murders <- mutate(murders, population_in_millions = population / 10^6)
```

We can write `population` rather than `murders$population`. 
The function `mutate` knows we are grabbing columns from `murders`.

Use the function `mutate` to add a murders column named `rate` with the per 100,000 murder rate as in the example code above. Make sure you redefine `murders` as done in the example code above ( murders <- [your code]) so we can keep using this variable.
```{r}
murders <- mutate(murders, rate = total / population * 100000)
```

2\. If `rank(x)` gives you the ranks of `x` from lowest to highest, `rank(-x)` gives you the ranks from highest to lowest. Use the function `mutate` to add a column `rank` containing the rank, from highest to lowest murder rate. Make sure you redefine `murders` so we can keep using this variable.

```{r}
murders <- mutate(murders, rank = rank(rate))
murders
```


3\. With __dplyr__, we can use `select` to show only certain columns. For example, with this code we would only show the states and population sizes:

```{r, eval=FALSE}
select(murders, state, population) %>% head()
```

Use `select` to show the state names and abbreviations in `murders`. Do not redefine `murders`, just show the results.
```{r}
select(murders, state, abb)
#다음 단원에 나오는것
select(murders, state, abb) %>% head()
```


4\. The __dplyr__ function `filter` is used to choose specific rows of the data frame to keep. Unlike `select` which is for columns, `filter` is for rows. For example, you can show just the New York row like this:

```{r, eval=FALSE}
filter(murders, state == "New York")
```

You can use other logical vectors to filter rows.

Use `filter` to show the top 5 states with the highest murder rates. After we add murder rate and rank, do not change the murders dataset, just show the result. Remember that you can filter based on the `rank` column.

```{r}
filter(murders, rank <= 5)
``` 

 
5\. We can **remove rows using the `!=` operator**. For example, to remove Florida, we would do this:

```{r, eval=FALSE}
no_florida <- filter(murders, state != "Florida")
```

Create a new data frame called `no_south` that removes states from the South region. How many states are in this category? You can use the function `nrow` for this.
```{r}
no_south <- filter(murders, region != "South")
nrow(no_south)
```


6\. We can also use `%in%` to filter with __dplyr__. You can therefore see the data from New York and Texas like this:

```{r, eval=FALSE}
filter(murders, state %in% c("New York", "Texas"))
```

Create a new data frame called `murders_nw` with only the states from the Northeast and the West.  How many states are in this category? 
```{r}
murders_nw <- filter(murders, region %in% c("Northeast", "West"))
murders_nw
nrow(murders_nw)
```


7\. Suppose you want to live in the Northeast or West **and** want the murder rate to be less than 1. We want to see the data for the states satisfying these options. Note that you can use logical operators with `filter`. Here is an example in which we filter to keep only small states in the Northeast region.

```{r, eval=FALSE}
filter(murders, population < 5000000 & region == "Northeast")
```

Make sure `murders` has been defined with `rate` and `rank` and still has all states. Create a table called `my_states` that contains rows for states satisfying both the conditions: it is in the Northeast or West and the murder rate is less than 1.  Use `select` to show only the state name, the rate, and the rank.
```{r}
murders <- mutate(murders, rate = total / population * 100000)
murders <- mutate(murders, rank = rank(rate))
my_states <- filter(murders, region %in% c("Northeast", "West") & rate < 1)
select(my_states, state, rate, rank)
```

## 3.3 The pipe: 코드의 실행 순서, 로직의 순서를 설정해보기: `%>%`

With __dplyr__ we can perform a series of operations, for example `select` and then `filter`, by sending the results of one function to another using what is called the _pipe operator_: `%>%`. Some details are included below. 

We wrote code above to show three variables (state, region, rate) for states that have murder rates below 0.71. To do this, we defined the intermediate object `new_table`. In __dplyr__ we can write code that looks more like a description of what we want to do without intermediate objects: 

$$ \mbox{original data }
\rightarrow \mbox{ select }
\rightarrow \mbox{ filter } $$


For such an operation, we can use the pipe `%>%`. The code looks like this:

```{r}
murders %>% select(state, region, rate) %>% filter(rate <= 0.71)
```

This line of code is equivalent to the two lines of code above. What is going on here? 

In general, the pipe _sends_ the result of the left side of the pipe to be the first argument of the function on the right side of the pipe. Here is a very simple example:

```{r}
16 %>% sqrt()
```
We can continue to pipe values along:

```{r}
16 %>% sqrt() %>% log2()
```
The above statement is equivalent to `log2(sqrt(16))`.

Remember that the pipe sends values to the first argument, so we can define other arguments as if the first argument is already defined:

```{r}
16 %>% sqrt() %>% log(base = 2)
```

Therefore, when using the pipe with data frames and __dplyr__, we no longer need to specify the required first argument since the __dplyr__ functions we have described all take the data as the first argument. In the code we wrote:

```{r, eval=FALSE}
murders %>% select(state, region, rate) %>% filter(rate <= 0.71)
```
`murders` is the first argument of the `select` function, and the new data frame (formerly `new_table`) is the first argument of the `filter` function.

Note that the pipe works well with functions where the first argument is the input data. Functions in __tidyverse__ packages like __dplyr__ have this format and can be used easily with the pipe.

## Exercises

1\. **The pipe `%>%` can be used to perform operations sequentially** without having to define intermediate objects. Start by redefining murder to include rate and rank.

```{r, eval=FALSE}
#mutate함수로 rate, rank column 추가
murders <- mutate(murders, rate =  total / population * 100000, rank = rank(-rate))
```

In the solution to the previous exercise, we did the following:
```{r, eval=FALSE}
my_states <- filter(murders, region %in% c("Northeast", "West") & rate < 1)
select(my_states, state, rate, rank)
```

pipe `%>%`을 쓰면 `my_states`같은 variable지정 없이 sequentially하게 코드진행이 가능

 We therefore could have mutated and selected in the same line like this:

```{r, eval=FALSE}
mutate(murders, rate =  total / population * 100000, 
       rank = rank(-rate)) %>%
  select(state, rate, rank)
```

??`select`에 data frame argument안가져도 되네요? -> 이미 `%>%`으로 conduct되었기 때문이죠.

Repeat the previous exercise, but now instead of creating a new object, show the result and only include the state, rate, and rank columns. Use a pipe `%>%` to do this in just one line.
```{r}
murders
filter(murders, region %in% c("Northeast", "West") & rate < 1) %>% select(state, rate, rank)
```

2\. Reset `murders` to the original table by using `data(murders)`. Use a pipe to create a new data frame called `my_states` that considers only states in the Northeast or West which have a murder rate lower than 1, and contains only the state, rate and rank columns. The pipe should also have four components separated by three `%>%`. The code should look something like this:
    
```{r, eval=FALSE}
#들여쓰기도 주의하세요.
my_states <- murders %>%
  mutate SOMETHING %>% 
  filter SOMETHING %>% 
  select SOMETHING
```

```{r, eval=FALSE}
#아래 코드는 오류 떠버림 이미 로직 구조상 murders를 assign해서 다음 구조에서도 murders를 넣으면 오류가 되어버림
data(murders)
my_states <- murders %>%
  mutate(murders, rate =  total / population * 100000, rank = rank(-rate)) %>%
  filter(murders, region %in% c("Northeast", "West") & rate < 1) %>%
  select(state, rate, rank)
```

```{r}
data(murders)
my_states <- murders %>% 
  mutate(rate =  total / population * 100000, rank = rank(-rate)) %>%
  filter(region %in% c("Northeast", "West") & rate < 1) %>%
  select(state, rate, rank)
my_states
```
